HerMES: ALMA Imaging of {\it Herschel}$^{\dagger}$-selected Dusty Star-forming Galaxies

### 2015-04-15 LaTeX/ms.tex
Revised draft
Nearly ready for submission…

%./authors_list hermes_authors_data_dr1_20121108.txt apj rsb dr fialkov hayward cowley almalens

\author{R.~S.~Bussmann\altaffilmark{1},
D.~Riechers\altaffilmark{1},
A.~Fialkov\altaffilmark{2},
C.~Hayward\altaffilmark{3,4},
W.~Cowley\altaffilmark{5},
J.~Bock\altaffilmark{6,7},
J.~Calanog\altaffilmark{8},
A.~Cooray\altaffilmark{8},
F.~De Bernardis\altaffilmark{8},
R.~Hopwood\altaffilmark{9},
M.~Jarvis\altaffilmark{10},
C.~Lacey\altaffilmark{5},
A.~Loeb\altaffilmark{4},
S.~J.~Oliver\altaffilmark{11},
I.~P{\'e}rez-Fournon\altaffilmark{12,13},
I.~G.~Roseboom\altaffilmark{11,14},
A.~J.~Smith\altaffilmark{11},
L.~Wang\altaffilmark{11},
J.~Wardlow\altaffilmark{15}}
\altaffiltext{$\dagger$}{Herschel is an ESA space observatory with science
instruments provided by European-led Principal Investigator consortia and with
important participation from NASA.}
\altaffiltext{1}{Department of Astronomy, Space Science Building, Cornell University, Ithaca, NY, 14853-6801}
\altaffiltext{2}{Departement de Physique, Ecole Normale Sup erieure, CNRS, 24 rue Lhomond, Paris, 75005 France}
\altaffiltext{3}{TAPIR 350-17, California Institute of Technology, 1200 E. California Boulevard, Pasadena, CA 91125}
\altaffiltext{4}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
\altaffiltext{5}{Institute for Computational Cosmology, Department of Physics, University of Durham, South Road, Durham, DH1 3LE, UK}
\altaffiltext{6}{California Institute of Technology, 1200 E. California Blvd., Pasadena, CA 91125}
\altaffiltext{7}{Jet Propulsion Laboratory, 4800 Oak Grove Drive, Pasadena, CA 91109}
\altaffiltext{8}{Dept. of Physics \& Astronomy, University of California, Irvine, CA 92697}
\altaffiltext{9}{Astrophysics Group, Imperial College London, Blackett Laboratory, Prince Consort Road, London SW7 2AZ, UK}
\altaffiltext{10}{Centre for Astrophysics Research, University of Hertfordshire, College Lane, Hatfield, Hertfordshire AL10 9AB, UK}
\altaffiltext{11}{Astronomy Centre, Dept. of Physics \& Astronomy, University of Sussex, Brighton BN1 9QH, UK}
\altaffiltext{12}{Instituto de Astrof{\'\i}sica de Canarias (IAC), E-38200 La Laguna, Tenerife, Spain}
\altaffiltext{13}{Departamento de Astrof{\'\i}sica, Universidad de La Laguna (ULL), E-38205 La Laguna, Tenerife, Spain}
\altaffiltext{14}{Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK}
\altaffiltext{15}{Dark Cosmology Centre, Niels Bohr Institute, University of Copenhagen, Juliane Maries Vej 30, 2100 Copenhagen, Denmark}

@@

    The {\it Herschel} Multi-tiered Extragalactic Survey (HerMES) has
    identified large numbers of dusty star-forming galaxies (DSFGs) over a wide
    range in redshift.  A detailed understanding of these DSFGs is hampered by
    the poor spatial resolution of {\it Herschel}.  We present 870$\,\mu$m
    0$\farcs$45 imaging obtained in Cycle~0 with the Atacama Large
    Millimeter/submillimeter Array (ALMA) of a sample of 29 HerMES DSFGs.  The
    ALMA imaging reveals that these DSFGs comprise a total of 62 sources (down
    to the $5\sigma$ limit in our ALMA sample; $\sigma \approx 0.2\,$mJy).
    Optical or near-infrared imaging indicates that 36 of the ALMA sources
    experience a significant flux boost from gravitational lensing ($\mu >
    1.1$), but only 6 are strongly lensed and show multiple images.  Combined
    with our previous work on brighter {\it Herschel} sources, the lens models
    presented here constrain the shape of the intrinsic luminosity function for
    DSFGs to have a break near 8$\,$mJy at 880$\,\mu$m with a very steep fall
    off at higher flux densities.  We introduce and make use of {\sc
    uvmcmcfit}, a general purpose and publicly available Markov chain Monte
    Carlo visibility plane analysis tool to analyze the source properties.
    Nearly 70\% of the {\it Herschel} sources break down into multiple ALMA
    counterparts, consistent with previous research indicating that the
    multiplicity rate is high in bright sources discovered in single-dish
    sub-mm or FIR surveys.  The ALMA counterparts to our {\it Herschel} targets
    are located significantly closer to each other than ALMA counterparts to
    sources found in the LABOCA ECDFS Submillimeter Survey.  Theoretical models
    underpredict the excess number of sources with small separations seen in
    our ALMA sample.  The high multiplicity rate and low projected separations
    between sources seen in our sample argue in favor of interactions and
    mergers plausibly driving both the prodigious emission from the brightest
    DSFGs as well as the sharp downturn above $S_{880} = 8\,$mJy.

@@

We used positional priors based on the ALMA data presented in this paper to
obtain the best possible estimates of the total SPIRE flux densities for each
{\it Herschel} source.  We also used {\it Spitzer}/MIPS
\citep{2004ApJS..154...25R} imaging to take into consideration the presence of
nearby 24$\,\mu$m sources that are not detected by ALMA but may still
contribute to the 250$\,\mu$m emission detected by {\it Herschel}.  Additional
details on our methodology are provided in Section~\ref{sec:photometry}.  The
SPIRE flux densities measured in this way represent our ``fiducial'' flux
densities and are presented in Table~\ref{tab:positions}.  Interested readers
may refer to Table~\ref{tab:photometry} for a comparison of the fiducial,
StarFinder and SUSSEXtractor flux densities in tabular form.

@@

Figure~\ref{fig:delens} shows the observed (i.e., apparent) and intrinsic
(i.e., de-lensed) distributions of $S_{870}$, $r_{\rm s}$, angular separation,
and $q_{\rm s}$.  Here, angular separation is the angular distance between an
ALMA source and the centroid of all the ALMA sources for a given {\it Herschel}
DSFG.  Lensing has the strongest effect on $S_{870}$: the median flux density
in the {\it Herschel}-ALMA sample drops by a factor of 1.6 when lensing is
taken into account. A two-sided Kolmogorov-Smirnov (KS) test yields a $p$-value
of 0.044, suggesting the apparent and intrinsic flux density distributions are
inconsistent with being drawn from the same parent population.  Even if
strongly lensed sources are removed from the sample, the median intrinsic flux
density is 1.3 times lower than the median apparent flux density.  If we only
consider examples of weak lensing (i.e., removing the unlensed sources), the
factor rises back to 1.6.  These factors will be significant sources of error
if they are incorrectly ignored.  When discussing the intrinsic properties of
bright sources \citep[including their luminosity functions,
e.g.][]{Wyithe:2011rm} discovered in wide-field FIR or mm surveys, it is
critical to consider the effects of lensing.

@@

Finally, the brightest single source in the {\it Herschel}-ALMA sample is
HADFS11.0, with an intrinsic flux density of $S_{870} = 17.5 \pm
0.4\,$mJy.  However, there are also two objects with multiple sources that
have separations smaller than 1$\arcsec$, which have summed flux densities
comparable to this; namely HADFS02 (16.8$\,$mJy) and HECDFS13 (15.3$\,$mJy).  This is
approaching the values found in the most extreme systems, such as GN20
\citep[20.6$\,$mJy,][]{2006MNRAS.370.1185P} and HFLS3
\citep[15-20$\,$mJy;][]{Riechers:2013lr, Cooray:2014rm, Robson:2014xy}.  It is
a level that is extremely difficult to reproduce in simulations
\citep[e.g.,][]{Narayanan:2010lr}.  One possibility is that the objects with
multiple sources represent blends of physically unassociated systems.  Testing
this possibility requires redshift determinations of each source and is beyond
the scope of this paper.

@@

\caption{ {\it Left}: Spatial distribution of sources with multiple
counterparts found in our {\it Herschel}-ALMA sample (green squares), in ALESS
(pink diamonds), and in mock catalogs from \citet{HB13} (color scale).  Sources
identified in our {\it Herschel}-ALMA sample lie much closer to each other than
they do in either ALESS or the \citet{HB13} simulations.  {\it Right}: Number
of ALMA sources per annular area as a function of angular separation from the
ALMA centroid.  Results are shown for our ALMA sample (thick green line), ALESS
(thick pink line), the \citet{HB13} simulations (thick blue line), and our {\it
Herschel}-ALMA sample as would have been seen with ALESS resolution and
sensitivity (thick orange line).  We also show the range of separations that
would be seen if sources were randomly distributed within the ALMA field of
view (green hatched region with solid and dashed green lines).  The DSFGs in
our {\it Herschel}-ALMA sample show a much stronger excess on angular
separation scales $<2\arcsec$ compared to ALESS and the \citet{HB13}
simulations, even when taking into account the difference in sensitivity and
spatial resolution between our ALMA observations and those of ALESS.  }
\label{fig:dNdA}

@@

An excess of sources with small separations from each other could be an
indication of interacting or merging systems.  However, it is also possible
that the sources are merely unrelated galaxies that appear blended due to
projection effects \citep{HB13}.  Spatially resolved spectroscopy is necessary
to answer this question definitively, but is not currently available.  Instead,
to investigate these possibilities further, we make use of mock catalogs of
DSFGs that are based on numerical simulations and presented by \citet{HB13}.
We summarize the methodology used to generate $dN/dA$ values from the mock
catalogs here and refer the reader to \citet{HB13} for full details.

@@

The $dN/dA$ values found in the mock catalogs are shown by the
thick blue line in Figure \ref{fig:dNdA}.  There is a significant increase in
$dN/dA$ on separations smaller than $\approx 0\farcs5$, but the amplitude of
the increase is much lower than is apparent in our {\it Herschel}-ALMA sample.

@@

@@

Both models tested in this paper exhibit a sharp transition from low
probability to high probability of being lensed, consistent with the data.
However, there are significant differences in where this transition flux
density, $S_{\rm trans}$, occurs --- i.e., where $P(\mu>\mu_{870}$ > 2).  In
the data, the logistic regression fit yields $S_{\rm trans} = 24\,$mJy,
whereas the models based on the ALESS and COSMOS luminosity functions yield
$S_{\rm trans} = 37\,$mJy $S_{\rm trans} = 69\,$mJy, respectively.

@@

This analysis highlights the difficulty encountered with the luminosity
function based on the COSMOS data: unlensed sources with $S_{870} > 50\,$mJy
are over-predicted and lensed sources with $S_{870} < 50\,$mJy are
under-predicted.  If the ALESS luminosity function continues to be supported by
the evidence as additional data are obtained, the implications are significant.
We should then expect to find $\approx 3$ sources satisfying $S_{870} >
10\,$mJy in a 1$\,$deg$^2$ survey.  This is about a factor of 7 lower than
typical measurements from single-dish, broad-beam studies
\citep[e.g.,][]{Weis:2009ly}.  This suggests that very luminous galaxies such
as GN20 and HFLS3 may be much more rare than previously thought.

@@

    \item 36/62 ALMA sources experience significant amplification from a nearby
        foreground galaxy ($\mu_{870} > 1.1$).  The median amplification in the
        sample is $\mu_{870} = 1.6$.  Only 6 sources show morphology typical of
        strong gravitational lensing and could be identified as lenses from the
        ALMA imaging alone.  A multi-wavelength approach is critical to
        identifying structure along the line of sight and determining an
        unbiased measurement of the flux densities in our sample.

@@

    \item When a {\it Herschel} source comprises multiple ALMA counterparts,
        these counterparts are typically located within 2$\arcsec$ of each
        other.  Their separations are significantly smaller than ALMA
        counterparts to ALESS sources as well as simulated sources from
        \citet{HB13}.  This conclusion remains true even when we degrade our
        ALMA observations to match the spatial resolution, sensitivity, and
        {\it uv} coverage of the ALESS observations.

@@

In the future, higher spatial resolution imaging is needed to investigate the
morphologies of individual ALMA sources.  Tidal tails, multiple nuclei, and
other signs of mergers and interactions should become evident at $0\farcs1$
resolution.  In addition, molecular spectroscopy will be critical to determine
distances to and dynamics of individual ALMA sources and hence characterize
what fraction of {\it Herschel} sources are actually physically associated with
each other (and not just a result of projection effects along the line of
sight).  %Molecular spectroscopy will also provide critical information about
%the inter-stellar medium in these galaxies, yielding insight into the process
%of how gas turns into stars.

@@

\clearpage
\input{table_photometry}

>>>>

%./authors_list hermes_authors_data_dr1_20121108.txt apj rsb dr fialkov scudders hayward cowley almalens
\author{R.~S.~Bussmann\altaffilmark{1},
D.~Riechers\altaffilmark{1},
A.~Fialkov\altaffilmark{2},
J.~Scudders\altaffilmark{3},
C.~Hayward\altaffilmark{4,5},
W.~Cowley\altaffilmark{6},
J.~Bock\altaffilmark{7,8},
J.~Calanog\altaffilmark{9},
S.~C.~Chapman\altaffilmark{10},
A.~Cooray\altaffilmark{9},
F.~De Bernardis\altaffilmark{9},
Hai~Fu\altaffilmark{11},
R.~Gavazzi\altaffilmark{12},
R.~Hopwood\altaffilmark{13},
R.~J.~Ivison\altaffilmark{14,15},
M.~Jarvis\altaffilmark{16},
C.~Lacey\altaffilmark{6},
A.~Loeb\altaffilmark{5},
S.~J.~Oliver\altaffilmark{3},
I.~P{\'e}rez-Fournon\altaffilmark{17,18},
D.~Rigopoulou\altaffilmark{19,20},
I.~G.~Roseboom\altaffilmark{3,15},
Douglas~Scott\altaffilmark{21},
A.~J.~Smith\altaffilmark{3},
L.~Wang\altaffilmark{3},
J.~Wardlow\altaffilmark{22}}
\altaffiltext{$\dagger$}{Herschel is an ESA space observatory with science
instruments provided by European-led Principal Investigator consortia and with
important participation from NASA.}
\altaffiltext{1}{Department of Astronomy, Space Science Building, Cornell University, Ithaca, NY, 14853-6801}
\altaffiltext{2}{Departement de Physique, Ecole Normale Sup erieure, CNRS, 24 rue Lhomond, Paris, 75005 France}
\altaffiltext{3}{Astronomy Centre, Dept. of Physics \& Astronomy, University of Sussex, Brighton BN1 9QH, UK}
\altaffiltext{4}{TAPIR 350-17, California Institute of Technology, 1200 E. California Boulevard, Pasadena, CA 91125}
\altaffiltext{5}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
\altaffiltext{6}{Institute for Computational Cosmology, Department of Physics, University of Durham, South Road, Durham, DH1 3LE, UK}
\altaffiltext{7}{California Institute of Technology, 1200 E. California Blvd., Pasadena, CA 91125}
\altaffiltext{8}{Jet Propulsion Laboratory, 4800 Oak Grove Drive, Pasadena, CA 91109}
\altaffiltext{9}{Dept. of Physics \& Astronomy, University of California, Irvine, CA 92697}
\altaffiltext{10}{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK}
\altaffiltext{11}{Department of Physics and Astronomy, The University of Iowa, 203 Van Allen Hall, Iowa City, IA 52242}
\altaffiltext{12}{Institut d'Astrophysique de Paris, UMR 7095, CNRS, UPMC Univ. Paris 06, 98bis boulevard Arago, F-75014 Paris, France}
\altaffiltext{13}{Astrophysics Group, Imperial College London, Blackett Laboratory, Prince Consort Road, London SW7 2AZ, UK}
\altaffiltext{14}{UK Astronomy Technology Centre, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK}
\altaffiltext{15}{Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK}
\altaffiltext{16}{Centre for Astrophysics Research, University of Hertfordshire, College Lane, Hatfield, Hertfordshire AL10 9AB, UK}
\altaffiltext{17}{Instituto de Astrof{\'\i}sica de Canarias (IAC), E-38200 La Laguna, Tenerife, Spain}
\altaffiltext{18}{Departamento de Astrof{\'\i}sica, Universidad de La Laguna (ULL), E-38205 La Laguna, Tenerife, Spain}
\altaffiltext{19}{RAL Space, Rutherford Appleton Laboratory, Chilton, Didcot, Oxfordshire OX11 0QX, UK}
\altaffiltext{20}{Department of Astrophysics, Denys Wilkinson Building, University of Oxford, Keble Road, Oxford OX1 3RH, UK}
\altaffiltext{21}{Department of Physics \& Astronomy, University of British Columbia, 6224 Agricultural Road, Vancouver, BC V6T~1Z1, Canada}
\altaffiltext{22}{Dark Cosmology Centre, Niels Bohr Institute, University of
Copenhagen, Juliane Maries Vej 30, 2100 Copenhagen, Denmark}

@@

    The {\it Herschel} Multi-tiered Extragalactic Survey (HerMES) has
    identified large numbers of dusty star-forming galaxies (DSFGs) over a wide
    range in redshift.  A detailed understanding of these DSFGs is hampered by
    the poor spatial resolution of {\it Herschel}.  We present 870$\,\mu$m
    0$\farcs$45 imaging obtained in Cycle~0 with the Atacama Large
    Millimeter/submillimeter Array (ALMA) of a sample of 29 HerMES DSFGs.  The
    ALMA imaging reveals that these DSFGs comprise a total of 62 sources (down
    to the $5\sigma$ limit in our ALMA sample; $\sigma \approx 0.2\,$mJy).
    Optical or near-infrared imaging indicates that 36 of the ALMA sources
    experience a significant flux boost from gravitational lensing ($\mu >
    1.1$), but only 6 are strongly lensed and show multiple images.  We
    introduce and make use of {\sc uvmcmcfit}, a general purpose and publicly
    available Markov chain Monte Carlo visibility plane analysis tool to
    analyze the source properties.  Combined with our previous work on brighter
    {\it Herschel} sources, the lens models presented here tentatively favor
    intrinsic luminosity functions for DSFGs with a break near 8$\,$mJy at
    880$\,\mu$m and a steep fall off at higher flux densities.  Nearly 70\% of
    the {\it Herschel} sources break down into multiple ALMA counterparts,
    consistent with previous research indicating that the multiplicity rate is
    high in bright sources discovered in single-dish sub-mm or FIR surveys.
    The ALMA counterparts to our {\it Herschel} targets are located
    significantly closer to each other than ALMA counterparts to sources found
    in the LABOCA ECDFS Submillimeter Survey.  Theoretical models underpredict
    the excess number of sources with small separations seen in our ALMA
    sample.  The high multiplicity rate and low projected separations between
    sources seen in our sample argue in favor of interactions and mergers
    plausibly driving both the prodigious emission from the brightest DSFGs as
    well as the sharp downturn above $S_{880} = 8\,$mJy.

@@

We used positional priors based on the ALMA data presented in this paper to
obtain the best possible estimates of the total SPIRE flux densities for each
{\it Herschel} source.  We also used {\it Spitzer}/MIPS
\citep{2004ApJS..154...25R} imaging to take into consideration the presence of
nearby 24$\,\mu$m sources that are not detected by ALMA but may still
contribute to the 250$\,\mu$m emission detected by {\it Herschel}.  Additional
details on our methodology are provided in Section~\ref{sec:photometry}.  The
SPIRE flux densities measured in this way represent our ``fiducial'' flux
densities and are presented in Table~\ref{tab:position}.  Interested readers
may refer to Table~\ref{tab:photometry} for a comparison of the fiducial,
StarFinder and SUSSEXtractor flux densities in tabular form.

@@

Figure~\ref{fig:delens} shows the observed (i.e., apparent) and intrinsic
(i.e., de-lensed) distributions of $S_{870}$, $r_{\rm s}$, angular separation,
and $q_{\rm s}$.  Here, angular separation is the angular distance between an
ALMA source and the centroid of all the ALMA sources for a given {\it Herschel}
DSFG.  Lensing has the strongest effect on $S_{870}$: the median flux density
in the {\it Herschel}-ALMA sample drops by a factor of 1.6 when lensing is
taken into account. A two-sided Kolmogorov-Smirnov (KS) test yields a $p$-value
of 0.044, suggesting the apparent and intrinsic flux density distributions are
inconsistent with being drawn from the same parent population.  Even if
strongly lensed sources are removed from the sample, the median intrinsic flux
density is 1.3 times lower than the median apparent flux density.  Removing the
unlensed sources from consideration pushes this factor back to 1.6.  At these
levels, failing to correct for amplification due to gravitational lensing will
be a significant source of error, since the absolute calibration uncertainty is
typically of order 5-10\%.  When discussing the intrinsic properties of bright
sources \citep[including their luminosity functions, e.g.][]{Wyithe:2011rm}
discovered in wide-field FIR or mm surveys, it is critical to consider the
effects of lensing.

@@

Finally, the brightest source in the {\it Herschel}-ALMA sample is
HADFS11.0, with an intrinsic flux density of $S_{870} = 17.5 \pm 0.4\,$mJy.
However, there are also two objects with multiple sources that have separations
smaller than 1$\arcsec$, which have summed flux densities comparable to this;
namely HADFS02 (16.8$\,$mJy) and HECDFS13 (15.3$\,$mJy).  This is approaching
the values found in the most extreme systems, such as GN20
\citep[20.6$\,$mJy,][]{2006MNRAS.370.1185P} and HFLS3
\citep[15-20$\,$mJy;][]{Riechers:2013lr, Cooray:2014rm, Robson:2014xy}.  It is
a level that is extremely difficult to reproduce in simulations
\citep[e.g.,][]{Narayanan:2010lr}.  One possibility is that the objects with
multiple sources represent blends of physically unassociated systems.  Testing
this possibility requires redshift determinations of each source and is beyond
the scope of this paper.

@@

\caption{ {\it Left}: Spatial distribution of sources with multiple
counterparts found in our {\it Herschel}-ALMA sample (green squares), in ALESS
(pink diamonds) and mock catalogs from \citet{HB13} and \citet{Cowley:2015lr}
(blue plus signs and orange crosses, respectively).  Sources identified in our
{\it Herschel}-ALMA sample lie much closer to each other than they do in either
ALESS or the \citet{HB13} simulations.  {\it Right}: Number of ALMA sources per
annular area as a function of angular separation from the ALMA centroid.
Symbols and colors are as in left panel.  We also show how our {\it
Herschel}-ALMA sample would appear if it had been observed with ALESS
resolution and sensitivity (light green squares).  The range of separations
that would be seen if sources were randomly distributed within the ALMA field
of view is also shown (dark dashed line and hatched region).  The {\it
Herschel}-ALMA DSFGs show a significantly stronger excess on angular separation
scales $<2\arcsec$ compared to both ALESS and the \citet{HB13} simulations,
even when taking into account the difference in sensitivity and spatial
resolution between our ALMA observations and those of ALESS.  The simulations
from \citet{Cowley:2015lr} show better agreement with the data, likely due to
the more sophisticated treatment of blending compared to \citet{HB13}.}
\label{fig:dNdA}

@@

An excess of sources with small separations from each other could be an
indication of interacting or merging systems.  However, it is also possible
that the sources are merely unrelated galaxies that appear blended due to
projection effects \citep{HB13}.  Spatially resolved spectroscopy is necessary
to answer this question definitively, but is not currently available.  Instead,
to investigate these possibilities further, we make use of mock catalogs of
DSFGs that are based on numerical simulations and presented by \citet{HB13} and
\citet{Cowley:2015lr}.

We begin with the \citet{HB13} simulations, summarizing the methodology used to
generate the mock catalogs here and refering the reader to \citet{HB13} for
full details.

@@

The $dN/dA$ values found in the mock catalogs are shown by the thick blue line
and plus signs in Figure \ref{fig:dNdA}.  There is a significant increase in
$dN/dA$ on separations smaller than $\approx 0\farcs5$, but the amplitude of
the increase is much lower than is apparent in our {\it Herschel}-ALMA sample.

@@

To explore this possibility, we investigate mock catalogs based on the
methodology presented in \citet{Cowley:2015lr}.  Here, we give a brief summary
and refer the interested reader to \citet{Cowley:2015lr} for full details. An
updated version of the {\sc galform} \citep[e.g.][Lacey et al. in
preparation]{Cole:2000fk} semi-analytic galaxy formation model is used to
populate halo merger trees \citep[e.g.][]{Parkinson:2008qy, Jiang:2014lr}
derived from a Millennium style $N$-body dark matter only simulation
\citep{Springel:2005lr, Guo:2013lr} with WMAP7 cosmology
\citep{Komatsu:2011fk}.  Submm flux is calculated using a model based on the
radiative transfer.  Dust is assumed to exist in two components,  dense
molecular clouds and a diffuse ISM.  Energy absorbed from starlight by each
dust component is calculated self-consistently.  The dust is then assumed to
emit radiation as a modified blackbody, assuming thermal equilibrium.

Three randomly orientated 20 deg$^2$ lightcone catalogues are generated using
the method described in \citet{Merson:2013lr}.  We choose as the lower flux
limit for inclusion of simulated galaxies into our lightcone catalogue
$S_{500\mu\rm{m}}>0.1$ mJy, as this is the limit at which we recover 90 per
cent of the extragalactic background light (EBL) as predicted by our model (122
Jy~deg$^{-2}$). This is in excellent agreement with observations from the
\emph{COBE} satellite \citep[e.g.,][]{Puget:1996lr}. This ensures we have a
realistic 500 $\mu$m  background in our mock images.

Mock imaging is created by binning the lightcone galaxies onto a pixelated grid
which is then convolved with a 36$\arcsec$ FWHM Gaussian (corresponding to the
\emph{Herschel} SPIRE beam at 500$\,\mu$m).  The image is then constrained to
have a zero mean by the subtraction of a uniform background.  No instrumental
noise is added, nor are any further filtering procedures applied to the mock
image.  This procedure is repeated at 350$\,\mu$m and 250$\,\mu$m in order to
provide simulated \emph{Herschel} photometry, adjusting the FWHM of the
Gaussian PSF appropriately and changing the lower limit of inclusion into our
lightcone to ensure 90 per cent of the predicted EBL is recovered at each
wavelength.

Source positions are selected as maxima in the mock 250$\,\mu$m image, with the
position and flux of the source being determined by the maximal pixel.  To
simulate `deblended' \emph{Herschel} photometry we record the value of the
pixel located at the position of the 250$\,\mu$m maxima in the 350$\,\mu$m and
500$\,\mu$m images. We select all \emph{Herschel} sources satisfying
$S_{500\,\mu\rm{m}}>50\,$mJy and $z > 1$ to identify galaxies from our
lightcone catalogs within a 9$\arcsec$ radius of the source position, modelling
the ALMA primary beam profile as a Gaussian with an 18$\arcsec$ FWHM and a
maximum sensitivity of 1$\,$mJy.

The $dN/dA$ values derived from the \citet{Cowley:2015lr} mock catalogs are
shown by the thick orange line and crosses in Figure \ref{fig:dNdA}.  Here, the
amplitude of the increase in $dN/dA$ on separations smaller than $\approx
2\arcsec$ mimics the trend seen in the data.  However, there is a deficit of
multiple systems with separations of $0\farcs5$ or less compared to the {\it
Herschel}-ALMA sample.  This result suggests that a sophisticated treatment of
blending yields better agreement between simulations and observations but the
simulations still under-predict the number of multiple systems with small
separations.

Future work on the theoretical side should seek to determine if the application
of the \citet{Cowley:2015lr} blending algorithm to the \citet{HB13} simulations
yields similarly better agreement with the data.  On the observational side, it
is critical to establish whether {\it Herschel} sources with multiple ALMA
counterparts are physically related by measuring spectroscopic redshifts to
individual counterparts.  Fortunately, this is a viable project today with the
VLA and ALMA.

@@

Both models tested in this paper exhibit a sharp transition from low
probability to high probability of being lensed, consistent with the data.
However, there are significant differences in where this transition flux
density, $S_{\rm trans}$, occurs --- i.e., where $P(\mu>\mu_{870}$ > 2).  In
the data, the logistic regression fit yields $S_{\rm trans} = 24\pm3\,$mJy
(error accounts only for statistical uncertainty in $S_{870}$ and $\mu_{870}$),
whereas the models based on the ALESS and COSMOS luminosity functions yield
$S_{\rm trans} = 37\,$mJy $S_{\rm trans} = 69\,$mJy, respectively.

@@

This analysis highlights the difficulty encountered with the luminosity
function based on the COSMOS data: unlensed sources with $S_{870} > 50\,$mJy
are over-predicted and lensed sources with $S_{870} < 50\,$mJy are
under-predicted.  If the ALESS luminosity function continues to be supported by
the evidence as additional data are obtained, the implications are significant.
We should then expect to find $\approx 3$ sources satisfying $S_{870} >
10\,$mJy in a 1$\,$deg$^2$ survey.  This is about a factor of 7 lower than
typical measurements from single-dish, broad-beam studies
\citep[e.g.,][]{Weis:2009ly}.  This suggests that very luminous galaxies such
as GN20 and HFLS3 may be more rare than previously thought.

@@

    \item 36/62 ALMA sources experience significant amplification from a nearby
        foreground galaxy that is comparable to or greater than the absolute
        calibration uncertainty (i.e., $\mu_{870} > 1.1$).  The median
        amplification in the subset that experiences lensing is $\mu_{870} =
        1.6$.  Only 6 sources show morphology typical of strong gravitational
        lensing and could be identified as lenses from the ALMA imaging alone.
        A multi-wavelength approach is critical to identifying structure along
        the line of sight and determining an unbiased measurement of the flux
        densities in our sample.

@@

    \item When a {\it Herschel} source comprises multiple ALMA counterparts,
        these counterparts are typically located within 2$\arcsec$ of each
        other.  Their separations are significantly smaller than ALMA
        counterparts to ALESS sources as well as simulated sources from
        \citet{HB13} and \citet{Cowley:2015lr}, although the improved
        treatment of blending by the latter yields superior agreement with the
        data.  This conclusion remains true even when we degrade our
        ALMA observations to match the spatial resolution, sensitivity, and
        {\it uv} coverage of the ALESS observations.

@@

In the future, higher spatial resolution imaging is needed to investigate the
morphologies of individual ALMA sources.  Tidal tails, multiple nuclei, and
other signs of mergers and interactions should become evident at $0\farcs1$
resolution.  In addition, molecular spectroscopy will be critical to determine
distances to and dynamics of individual ALMA sources and hence characterize
what fraction of {\it Herschel} sources are actually physically associated with
each other (and not simply a result of projection effects along the line of
sight).  %Molecular spectroscopy will also provide critical information about
%the inter-stellar medium in these galaxies, yielding insight into the process
%of how gas turns into stars.

@@

%\clearpage
\input{table_photometry}
